% Chapter Template

\chapter{Pre-Processing and Post-Processing Scheme for Fluorescence Microscopy Images} % Main chapter title

\label{chap:Chapter7} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\textcolor{red}{There are many factors that degrade the quality of images. The knock-on effect is sub-optimal segmentation results. List the problems and show some images of them. What techniques exist to curb these negative effects? Although it is very common for preprocessing to be done before any further analysis, lack of a scheme. Where do we take this up from (after PSF deconvolution). Why is it non-trivial to design criteria for an ideal image to segment? What do we plan to accomplish in this section?}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Fluorescence Image Properties}
\label{sec:imageproperties}

\textcolor{red}{Make a relation to it's impact on segmentation quality. 
	Noise: type and mathematical model. 
	Extreme low contrast issues.
	Edge enhancement and completion}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Preprocessing Scheme}
\label{sec:preprocessscheme}


%----------------------------------------------------------------------------------------
%	SUBSECTION 1
%----------------------------------------------------------------------------------------

\subsection{Denoising}
\label{sec:PoissonDenoising}

\textbf{Removing useless channels}\\
\textbf{Poisson Noise Reduction via Total-Variation Denoising}

%----------------------------------------------------------------------------------------
%	SUBSECTION 2
%----------------------------------------------------------------------------------------

\subsection{Contrast Correction}
\label{sec:contrastcorrection}

\textbf{Attenuation and Amplification}

%----------------------------------------------------------------------------------------
%	SUBSECTION 3
%----------------------------------------------------------------------------------------

\subsection{Channel Mixing}
\label{sec:channelmixing}


%----------------------------------------------------------------------------------------
%	SUBSECTION 4
%----------------------------------------------------------------------------------------

\subsection{Intra-Region Smoothing and Edge Completion and Enhancement}
\label{sec:Diffusion}

\textbf{Coherence Enhancing Diffusion}\\
\textbf{Coherence Enhancing Diffusion with Optimised Rotational Invariance}

%----------------------------------------------------------------------------------------
%	SUBSECTION 5
%----------------------------------------------------------------------------------------

\subsection{Removal of Segmentation Artifacts}
\label{sec:RemovalArtifacts}

\textbf{Connected Components}

%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------

\section{Experimental Results}
\label{sec:preprocessschemeexperimentalresults}

%----------------------------------------------------------------------------------------
%	SECTION 4
%----------------------------------------------------------------------------------------

\section{Discussion}
\label{sec:preprocessschemediscussion}

